---
title: "R Notebook"
output: html_notebook
---

```{r}
source("utility.R")

load("R1_1634_168_live_txyn.rdata") 
file_name <- "R1_1634_168_live"

u <- scan("random168.txt")
# u <- scan("random18.txt")
u <- (u - 744)/1712
```
note: t is 'frame' in txyn (time, x, y, node). This may be mis-leading, but it affects other programs. 

done: R1_1433_168_dead.MP4_out_txyn.rdata
done: R1_1443_168_dead.MP4_out_txyn.rdata
done: R1_1453_168_dead.MP4_out_txyn.rdata
done: R1_1503_18_dead.MP4_out_txyn.rdata
skip: R1_1634_168_live_txyn.rdata # wired part at basal part, skip
skip: R1_1647_168_live_txyn.rdata # skip
skip: R1_1700_168_live_txyn.rdata # skip
done: R1_1755_168_live_crop_txyn.rdata # job
R1_1810_168_live_crop_txyn.rdata # skip, wired part at basal part
done: R1_1820_168_live_crop_txyn.rdata # job
done: R1_1829_168_live_crop_txyn.rdata # job

done: R1_1512_18_dead.MP4_out_txyn.rdata # job
d R1_1520_18_dead.MP4_out_txyn.rdata # missing tracking at tail
d R1_1530_18_dead.MP4_out_txyn.rdata # missing tracking at tail
d R1_1538_18_dead-003_s2_out_txyn.rdata # job 18:45 including memory f
d R1_1541_18_dead.MP4_out_txyn.rdata # missing tracking at tail
d R1_1550_18_dead.MP4_out_txyn.rdata # missing tracking at tail
d R1_1601_18_dead.MP4_out_txyn.rdata # missing tracking at tail

done: R1_1528_168_dead-002_s2_out_txyn.rdata

done: L1_1505_168_dead-010_50fps_out_txyn.rdata
done: L1_1515_168_dead-009_50fps_out_txyn.rdata
done: L1_1524_168_dead-008_50fps_out_txyn.rdata
done: L1_1533_168_dead-002_50fps_out_txyn.rdata

done: L1_1542_18_dead-003_50fps_out_txyn.rdata
done: L1_1551_18_dead-004_50fps_out_txyn.rdata
done: L1_1600_18_dead-006_50fps_out_txyn.rdata

done: R1_1351_168_dead.MP4_out_txyn.rdata
done: run on console; R1_1403_168_dead.MP4_out_txyn.rdata
done; 0731_0905 R1_1413_168_dead.MP4_out_txyn.rdata # # weird, but using median (avoiding NA), it succeeded
done: R1_1423_168_dead.MP4_out_txyn.rdata #  weird track path exist, see probe_tracked_path_R1_1423_168_dead.Rmd
d R1_1507_168_dead-017_s2_out_txyn.rdata # from 4000 to 10500 but need check, cannot determine the tail end
done: R1_1518_168_dead-008_s2_out_txyn.rdata
done: R1_1720_168_live_crop_txyn.rdata
done: R1_1732_168_live_crop_txyn.rdata
done: R1_1745_168_live_crop_txyn.rdata


# check head part

```{r}
txyn %>% 
  filter(node==20 & 0  < t & t < 500) %>% 
  ggplot(.) + 
  geom_line(aes(t, y), alpha=0.2) + 
  geom_point(aes(t, y)) 
  # geom_vline(xintercept=1)
```
seed 168 case:
> head(u, 20)
 [1] 1 1 0 0 0 1 1 1 1 1 1 0 1 0 0 0 1 0 1 1
        ^
        cut here

seed 18
> head(u, 20)
 [1] 0 1 0 0 0 0 0 0 0 0 1 0 1 1 1 1 0 0 1 1
      ^




# check tail part
```{r}
ggplot(txyn %>% filter(node==20 & t > (max(txyn$t)-200))) + 
  geom_line(aes(t, y), alpha=0.2) + 
  geom_point(aes(t, y)) 
  # geom_vline(xintercept=24975)
```
seed 168 case:
> tail(u, 20)
 [1] 1 1 1 0 0 0 0 0 0 0 1 1 0 0 0 1 0 1 1 1
                                      ^
                                      cut here
see 18 case:
> tail(u, 20)
 [1] 1 1 1 0 0 0 0 0 0 0 1 1 0 0 0 1 0 1 1 1
                                    


```{r}
# plot(u[(length(u)-20):length(u)], type="b")
```


# detect swiching timing
```{r}
dp <- 
  txyn %>% 
  filter(node==20 & 0 < t & t < 200) %>% 
  mutate(dy=c(0, abs(diff(y)))) %>% 
  mutate(peak = !is.na(find_peak(dy, 1)))  # threshold tuning
  
  ggplot(dp) + 
  geom_point(aes(t, y)) +
  geom_line(aes(t, y), alpha=0.2) +
  geom_point(aes(t, y), data=dp %>% filter(peak), col=2)
```



```{r}
txyn %>% 
  filter(node==20 & 0 < t & t < 200) %>% 
  mutate(dy=c(0, abs(diff(y)))) %>% 
  mutate(peak = !is.na(find_peak(dy, 1))) %>% # 
  filter(peak) %>% 
  head(1) %>% 
  .$t -> head_frame

head_frame <- head_frame -1
head_frame
```


```{r}
txyn %>% 
  filter(node==20 & t > (max(txyn$t)-100) & t <= (max(txyn$t)-0)) %>% 
  mutate(dy=c(0, abs(diff(y)))) %>% 
  mutate(peak = !is.na(find_peak(dy, 2))) %>%  # threshold tuning 
  ggplot(.) + 
  geom_point(aes(t, y)) +
  geom_line(aes(t, y), alpha=0.2) +
  geom_point(aes(t, y), data=. %>% filter(peak), col=2)
```


# (IMPORTANT) tail cut
```{r}
txyn %>% 
  filter(node==20 & t > (max(txyn$t)-100) & t <= (max(txyn$t)-0)) %>% 
  mutate(dy=c(0, abs(diff(y)))) %>% 
  mutate(peak = !is.na(find_peak(dy, 2))) %>% 
  filter(peak) %>% 
  tail(1) %>% 
  .$t -> tail_frame

tail_frame <- tail_frame - 8 - 3
tail_frame
```


From the txyn, we need to remove the corresponding head- and tail-part.


# automatically determine the init and last input change (0 to 1 or 1 to 0)

```{r}
head_diff <- head(diff(u), 20)
for (i in 1:20) {
  if (head_diff[i] != 0) {
    init_frame <- i + 1
    break; 
  }
}
init_frame

tail_diff <- rev(tail(diff(u), 20))
for (i in 1:20) {
  if (head_diff[i] != 0) {
    last_frames_num <- i + 1
    break;
  }
}
# last_frames_num
# u[(length(u)-last_frames_num+1):length(u)]
last_frame <- length(u) - last_frames_num
last_frame
uu <- as.integer(u[init_frame:last_frame])
head(uu)
tail(uu)
length(uu)

write(uu, file="input168.txt")
# write(uu, file="input18.txt")

uu <- scan("input168.txt")
# uu <- scan("input18.txt")
```

# time matching
```{r}
txyn %>%
  filter(t >= head_frame & t <= tail_frame) %>% 
  mutate(y=y-mean(y)) %>% 
  group_by(node) %>% 
  mutate(frame_t = t - head_frame + 1) %>%   # offset, t from 1
  mutate(time_in_u = approx(1:length(uu), n=length(frame_t))$y) %>% 
  mutate(time_sec=(time_in_u-1)*0.1) %>% # 0.1 sec for tau, one time step
  mutate(u = map_int(time_in_u, \(ui) { uu[ui] })) %>% 
  select(-t, -frame_t) %>% 
  ungroup() -> txynu
```


```{r}
ggplot(txynu %>% filter(time_sec < 8 & node == 20)) + 
  geom_line(aes(time_sec, y, col=as.character(u), group=node)) +
  geom_line(aes(time_sec, u, group=node)) +
  my_theme()
```

```{r}
ggplot(txynu %>% filter(200 < time_sec & time_sec < 205 & node == 10)) + 
  geom_line(aes(time_sec, y, col=as.character(u), group=node)) +
  geom_line(aes(time_sec, u, group=node)) +
  my_theme()
```



```{r}
ggplot(txynu %>% filter(time_sec < 8 & node == 20)) + 
  geom_line(aes(time_sec, c(0, diff(y)), col=as.character(u), group=node)) +
  geom_line(aes(time_sec, c(0, diff(u)) )) +
  # geom_line(aes(time_sec, u, group=node)) +
  my_theme()
```
The peak values must be preceded by the input peak value!!!

```{r}
ggplot(txynu %>% 
         filter(node==20 & 
                  time_sec > max(time_sec) - 7 & 
                  time_sec < max(time_sec))) + 
      geom_line(aes(time_sec, u)) +
    # geom_line(aes(time_sec, c(0, diff(u)) )) +
  geom_line(aes(time_sec, y, col=as.character(u), group=node)) +
  # geom_line(aes(time_sec, c(0, diff(y)), col=as.character(u), group=node)) +
  my_theme()
```


```{r}
ggplot(txynu %>% filter(node==20 & time_sec > max(time_sec) - 7 & time_sec < max(time_sec))) +
  geom_line(aes(time_sec, c(0, diff(y)), col=as.character(u), group=node)) +
  geom_point(aes(time_sec, c(0, diff(y)), col=as.character(u), group=node)) +  
  geom_line(aes(time_sec, c(0, diff(u)-0), group=node)) +  
  my_theme()
```

Inbetween the peaks, it is important to have the values. This tail part is most important to check.



# save txynu
```{r}
save(txynu, file=paste0(file_name, "_txynu.rdata"))
```


# check stable part
```{r}
load(file=paste0(file_name, "_txynu.rdata"))
```


How path length is changing? If extreme change happens, remove the paths.
```{r}
txynu %>% 
  group_by(time_in_u) %>% 
  summarise(max_node_num=max(node)) %>% 
  ggplot(.) + 
  geom_histogram(aes(max_node_num), bins=50)
```



# remove more than L
```{r}
L <- 350 # currently this is just set large number
load("/Users/boweiyu/Arm project/Alife paper/R1_1820_168_live_txynu.rdata")
d <- txynu
```

fix the L though all frames, from base point

```{r}
txynu %>% 
  filter(101 < time_sec & time_sec < 103) -> d

ggplot(d) + 
  geom_point(aes(x, y), pch=".") +
  geom_line(aes(x, y, group=time_sec), alpha=0.5) +
  my_theme() +
  coord_fixed()

```

```{r}
ggplot(d) + 
  geom_line(aes(time_sec, y, group=node, col=node), alpha=0.5) +
  my_theme() 

```

```{r}
d %>% group_by(node) %>% summarise(time_sum=sum(time_in_u)) %>% ggplot(.) + geom_point(aes(node, time_sum)) +
  geom_vline(xintercept=228)
```
paper
```{r}
library(dplyr)
library(ggplot2)


df_sum <- d %>%
  group_by(node) %>%
  summarise(time_sum = sum(time_in_u))


max_y    <- max(df_sum$time_sum)
max_node <- max(df_sum$node)


p <- ggplot(df_sum, aes(x = node, y = time_sum)) +
  geom_point() +
  geom_vline(xintercept = 228) +
  annotate(
    "text",
    x     = max_node - 65,        
    y     = max_y * 0.85,       
    label = "point = 228",
    hjust = 1,                    
    size  = 10                    
  ) +
  theme_classic() +
  theme(
    axis.title = element_text(size = 22),
    axis.text  = element_text(size = 20)
  ) +
  labs(x = "point", y = "accumulated time")


print(p)


ggsave(
  filename = "accumulated_time.png",
  plot     = p,
  dpi      = 300,
  width    = 8,
  height   = 5,
  units    = "in"
)



```

# set threshold
```{r}
node_select_th <- 110
d %>% 
  group_by(node) %>% 
  mutate(node=ifelse(node < node_select_th, node, NA)) %>% 
  ggplot(.) + 
  geom_line(aes(time_sec, y-node, group=node, col=node), alpha=0.5)
```



```{r}
equi_assign <- function(x, y, stable_path,
                        other_var, # tibble(time_sec, time_in_u, u, path_cum_len)
                        node_n, approx_n=500, na_th=10, plotout=F) {
  
  x <- x[stable_path==1]
  y <- y[stable_path==1]
  
  # other vars, only time information is returned when no coordinate values
  if (any(is.na(x)) | length(x) < na_th) {return(tibble(x=NA, y=NA, unique(other_var))) }

  z <- approx(x, y, n=approx_n)
  
  d <- tibble(x=z$x, y=z$y)
  d <- d %>% mutate(path_length=c(0, cumsum(sqrt(diff(x)^2 + diff(y)^2))))
  
  L <- d$path_length %>% max()
  
  equi_d <- seq(0, L, length.out=node_n)
  
  dd <- d %>%
    mutate(node=findInterval(d$path_length, equi_d, all.inside=T)) %>%
    group_by(node) %>%
    mutate(sub_node=1:length(node)) %>%
    mutate(node2=ifelse(sub_node==max(sub_node), node, 0)) %>%
    mutate(node=node2) %>%
    filter(node2 != 0) %>%
    select(x, y, node)
  
  dd2 <- bind_rows(tibble(x=d[1,]$x, y=d[1,]$y, node=0), dd) 
  dd2 <- bind_cols(dd2, other_var[1:(dim(dd2)[1]),])

  # if (plotout) {
  #   plot(
  #     ggplot(d) +
  #       geom_point(aes(x, y), pch=".", alpha=0.9) +
  #       geom_point(aes(x, y), pch=1, data=dd2)
  #   )
  # }
  return(dd2)
}
path_cumsum_length <- function(x, y) {
  c(0, cumsum(sqrt(diff(x)^2 + diff(y)^2)))
}

d %>%
  group_by(node) %>% 
    # added to remove the wiered proximal part
    # only for this?
  mutate(node=ifelse(node < node_select_th & node > 20, node, NA)) %>% 
  ungroup() %>% 
  group_by(time_in_u) %>% 
  mutate(path_cum_len=path_cumsum_length(x, y)) %>% 
  # filter(path_cum_len < L) %>% # filter しちゃうとパスが少なくなる
  mutate(stable_path=ifelse(path_cum_len < L, 1L, 0L)) -> d2
d2 %>% 
  mutate(max_path_len=max(path_cum_len)) %>% 
  # filter(max_path_len > L - 5) %>% # ここで、time frame が抜けていた
  reframe(equi_assign(x, y, stable_path,
                      other_var=tibble(time_sec, time_in_u, u), node_n=100, approx_n=500)) -> d3

ggplot(d3) + 
  geom_point(aes(x, y), pch=".") +
  geom_line(aes(x, y, group=time_sec), alpha=0.1) +
  my_theme() +
  coord_fixed()
```
0 proximal 

```{r}
ggplot(d3) + 
  geom_line(aes(time_in_u, y-node*2, group=node), alpha=0.5) +
  my_theme() 

```


# extract selected stable path

```{r}
# library(tictoc)
# # node_select_th <- 140
# tic()
# txynu %>%
#   group_by(node) %>%
#   mutate(node=ifelse(node < node_select_th, node, NA)) %>%
#   ungroup() %>%
#   group_by(time_in_u) %>%
#   mutate(path_cum_len=path_cumsum_length(x, y)) %>%
#   mutate(stable_path=ifelse(path_cum_len < L, 1L, 0L)) %>%
#   mutate(max_path_len=max(path_cum_len)) %>%
#   reframe(equi_assign(x, y, stable_path,
#                       other_var=tibble(time_sec, time_in_u, u),
#                       node_n=100, approx_n=500)) -> txynu2
# save(txynu2, file=paste0(file_name, "_txynu2.rdata"))
# toc()
```

This will take time.


```{r}
# ggplot(txynu2 %>% filter(400 < time_sec & time_sec < 410)) +
#   geom_line(aes(time_sec, y-node, group=node), alpha=0.1) +
#   geom_line(aes(time_sec, u*5)) +
#   my_theme()
```
















